Relocating a cluster of earthquakes using a single station

### 2011-12-06 paper2/paper2.tex
brought the new (hypoDD SVD based) figures into the main document - ensured paper compiles under the new git repository

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The bottom subplot shows the average minimum number of branches required to link the 2450 pairs.}
 \label{fig:optimisationresults-2Dsynth}
\end{figure}

@@

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The absence of the blue and red lines below 60\% and 30\% indicates a breakdown in the solutions
when all or best optimisation result(s) are considered, respectively.}
\label{fig:optimisationresults-3Dsynth}
\end{figure}

@@

\begin{figure*}
\includegraphics{diags/CalaverasLoc1.eps}
\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
308 events (column 2) and CWI example 1 (column 3).
Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
blue events are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}

@@

\begin{figure*}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
\caption{....}
\label{fig-HYPODDreducesstats}
\end{figure*}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
\caption{Statistics on coordinate differences for reduced station inversions. Differences
are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. The top subplot illustrates the number of constrainable
events in the CWI and hypoDD inversions as a function of the stations considered.}
\label{fig-statremoval_summarystats}
\end{figure}

@@

\begin{figure*}
\noindent\includegraphics{diags/CalaverasLoc5.eps}
\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
\label{fig-68Calaverasevents_ttandcoda1}
\end{figure*}

@@

\begin{figure}
\noindent\includegraphics{diags/CalaverasLoc6.eps}
\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
relocation only (i.e. no CWI) using ........}
\label{fig-68Calaverasevents_ttsubsetandcoda1}
\end{figure}

@@

\begin{figure*}
\includegraphics{diags/CalaverasLoc1.eps}
\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
308 events (column 2) and CWI example 1 (column 3).
Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
blue events are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}

\begin{figure*}
\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
\caption{HypoDD (SVD) with reduced stations.}
\label{fig-HYPODDreducesstats}
\end{figure*}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
\caption{Statistics on coordinate differences for reduced station inversions. Differences
are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. The top subplot illustrates the number of constrainable
events in the CWI and hypoDD inversions as a function of the stations considered.}
\label{fig-statremoval_summarystats}
\end{figure}

\begin{figure*}
\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
\caption{Combined HypoDD (SVD) and CWI: all stations and 5 stations.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}

>>>>

\begin{figure}
%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\noindent\includegraphics[width = 20pc]{diags/ressummary_2Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The bottom subplot shows the average minimum number of branches required to link the 2450 pairs.}
 \label{fig:optimisationresults-2Dsynth}
\end{figure}

@@

\begin{figure}
%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
\noindent\includegraphics[width = 20pc]{diags/ressummary_3Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The absence of the blue and red lines below 60\% and 30\% indicates a breakdown in the solutions
when all or best optimisation result(s) are considered, respectively.}
\label{fig:optimisationresults-3Dsynth}
\end{figure}

@@

%%=======================================================================================
% This is the original figure using HypoDD with LSQR
%\begin{figure*}
%\includegraphics{diags/CalaverasLoc1.eps}
%\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
%308 events (column 2) and CWI example 1 (column 3).
%Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
%blue events are shown for the purpose of orientation only.}
%\label{fig-69Calaverasevents_eg1}
%\end{figure*}

% Now we have the SVD version 
\begin{figure*}
\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
308 events (column 2) and CWI example 1 (column 3).
Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
blue events are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}
%%=======================================================================================

@@

%%=========================================================================
% this is the original version using hypoDD with LSQ
%\begin{figure*}
%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
%\caption{....}
%\label{fig-HYPODDreducesstats}
%\end{figure*}

% This is the version using hypoDD with SVD
\begin{figure*}
\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
\caption{HypoDD (SVD) with reduced stations.}
\label{fig-HYPODDreducesstats}
\end{figure*}
%%=========================================================================

%%=========================================================================
% This is the original version using hypoDD with LSQ
%\begin{figure}
%\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
%\caption{Statistics on coordinate differences for reduced station inversions. Differences
%are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
%locations for all 308 events. The top subplot illustrates the number of constrainable
%events in the CWI and hypoDD inversions as a function of the stations considered.}
%\label{fig-statremoval_summarystats}
%\end{figure}

% This is the version using hypoDD with SVD
\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
\caption{Statistics on coordinate differences for reduced station inversions. Differences
are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. The top subplot illustrates the number of constrainable
events in the CWI and hypoDD inversions as a function of the stations considered.}
\label{fig-statremoval_summarystats}
\end{figure}
%%=========================================================================

@@

%%=========================================================================
% This is the original version using hypoDD with LSQ
% This is only makes sense for LSQR so we remove it from this manuscript
%\begin{figure*}
%\noindent\includegraphics{diags/CalaverasLoc5.eps}
%\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
%levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
%\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
%column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
%\label{fig-68Calaverasevents_ttandcoda1}
%\end{figure*}
%%=========================================================================

@@

%%=========================================================================
% This is the original version using hypoDD with LSQ
%\begin{figure}
%\noindent\includegraphics{diags/CalaverasLoc6.eps}
%\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
%22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
%are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
%relocation only (i.e. no CWI) using ........}
%\label{fig-68Calaverasevents_ttsubsetandcoda1}
%\end{figure}

% This is the version using hypoDD with SVD
\begin{figure*}
\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
\caption{Combined HypoDD (SVD) and CWI: all stations and 5 stations.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}
%%=========================================================================

@@
